Application for Rethinking Foundations of Physics 2017

### 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Kick-off Talk: The Meaning of Quantum Probability} Just copy the paper to this section...

\item Going further we actually have to concede not just the infinite
  accuracy of the quantum state, but its very existence as a ``real''
  entity that exists independently of measurements and
  probabilities. The reasons for this second radical position are as
  follows. First arguments embedded in the proof of the Kochen-Specker
  theorem essentially rule out the existence of a sample space as the
  probabilities of events cannot be consistently expressed using core
  assignments to elements of the sample space. Second, the frequency
  interpretation of probability which is already problematic in the
  classical case, becomes untenable in the quantum case. In both
  cases, but much more in the quantum case, it is much more sensible
  to interpret probability in the Bayesian sense as ``lack of
  knowledge''. This, and similar arguments elegantly expressed by
  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
  suggest that the quantum state is more like an interactive system in
  computer science parlance. In other words, the state is only
  determined by its interactions with the environment or observers. A
  rough but useful analogy in the context of computer science would be
  a web server: the state of such a system cannot be said to exist
  independently of the interactions with clients; each interaction
  with a client determines a future state of the system and may affect
  future interactions. Crucially, each client may have a
  \emph{different} view of the web server that is consistent with
  their own history of interactions. This computational perspective
  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
  that asserts that the quantum state is subjective: each observer has
  a different view of the quantum system that is consistent with their
  previous observations and that allows that observer, independently
  of other observers, to assign beliefs (i.e., probabilities) to
  possible future interactions.

--- next section

@@

>>>>

\item Going further we actually have to concede not just the infinite accuracy
of the quantum state, but its very existence as a ``real'' entity
that exists independently of measurements and probabilities. The reasons
for this second radical position are as follows. First arguments embedded
in the proof of the Kochen-Specker theorem essentially rule out the
existence of a sample space as the probabilities of events cannot
be consistently expressed using core assignments to elements of the
sample space. Second, the frequency interpretation of probability
which is already problematic in the classical case, becomes untenable
in the quantum case. In both cases, but much more in the quantum case,
it is much more sensible to interpret probability in the Bayesian
sense as ``lack of knowledge''. This, and similar arguments elegantly
expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
suggest that the quantum state is more like an interactive system
in computer science parlance. In other words, the state is only determined
by its interactions with the environment or observers. A rough but
useful analogy in the context of computer science would be a web server:
the state of such a system cannot be said to exist independently of
the interactions with clients; each interaction with a client determines
a future state of the system and may affect future interactions. Crucially,
each client may have a \emph{different} view of the web server that
is consistent with their own history of interactions. This computational
perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
that asserts that the quantum state is subjective: each observer has
a different view of the quantum system that is consistent with their
previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.
\end{itemize}

\section{Kick-off Talk: The Meaning of Quantum Probability}

@@

\section{Kick-off Talk: The Reality of the Quantum State}

— next section
